Solutions to the potential for unintended conservation consequences of MPAs

### 2021-10-07 documents/03_marlin_paper.Rmd
adding in hyperallometry

---
title: "Solutions to the potential for unintended conservation consequences of MPAs"
author:
    - Daniel Ovando
    - Darcy Bradley
    - Lennon Thomas
    - Echelle Burns
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2: default
  bookdown::html_document2: default
bibliography: references.bib
params:
  run_name: ["v0.5"]
---

@@

Looking at the full
`r n_distinct(total_experiment_results$placement_id) * n_distinct(total_experiment_results$state_id)`
experiments run, the results were highly variable, with MPAs capable of
producing substantial conservation gains to substantial conservation
losses and everything in between. We do not focus into the individual
effects of particular variables as we found them to be highly dependent
on the exact question asked and the set of data included, and since we
cannot ascribe any actual likelihood to any individual state of nature
simulated here.

@@

>>>>

---
title: "Solutions to the potential for unintended conservation consequences of MPAs"
subtitle: Conditions for success and unintended consequences in pelagic MPA design
author:
    - Daniel Ovando
    - Darcy Bradley
    - Lennon Thomas
    - Echelle Burns
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2: default
  bookdown::html_document2: default
bibliography: references.bib
params:
  run_name: ["v0.5"]
---

@@

Looking at the full
`r n_distinct(total_experiment_results$placement_id) * n_distinct(total_experiment_results$state_id)`
experiments run, the results were highly variable, with MPAs capable of
producing substantial conservation gains to substantial conservation
losses and everything in between.

Design matters size matters species matters habitat matters
```{r}

compact_experiment_results %>%
  filter(prop_mpa < 1) %>%
  # filter(f_v_m > 1.5) %>%
  group_by(state_id, placement_id) %>%
  ggplot(aes(
    prop_mpa,
    pmin(2,biodiv / bau_biodiv -1),
    color =  sigma_habitat,
    group = interaction(placement_id, state_id)
  )) +
  geom_line(alpha = 0.25) +
  geom_hline(aes(yintercept = 0), linetype = 2, color = "red") +
  facet_grid(critter ~ placement_strategy) +
  scale_color_viridis_c(name = "Habitat Difference", guide = guide_colorbar(frame.colour = "black",ticks.colour = "black")) +
  scale_y_continuous(labels = scales::percent,"Change in SSB/SSB0 relative to BAU") +
  scale_x_continuous(labels = scales::label_percent(accuracy = 1), name = "MPA Size") +
  theme(legend.position = "top")

```{r}

critter_results <- compact_experiment_results %>%
  group_by(state_id, placement_id) %>%
  mutate(real_sigma_centroid = sd(centroid)) %>%
  mutate(delta_biodiv = pmin(2,biodiv / bau_biodiv - 1),
         loss = biodiv < bau_biodiv,
         rec_form = as.factor(rec_form)) %>% 
  mutate(critter = fct_relevel(critter,c("Tuna", "Marlin","Shark")),
         rec_form = fct_recode(rec_form, "Global DD, Rec. By Habitat" = "0", "Local DD, local Recruitment" = "1", "Local DD, Disperse Recruits" = "2", "Disperse Larvae, Poset-Settlement DD" = "3"))

reg_2 <-   rstanarm::stan_glm(
  loss ~   f_v_m  + critter + seasonal_movement + adult_movement_sigma + rec_form + recruit_movement_sigma + prop_mpa + sigma_habitat + spatial_allocation,
  family = binomial(),
  data = critter_results %>% filter(between(prop_mpa,.2,.4), placement_strategy == "area"),
  cores = 4,
  chains = 4
)

fig_11 <- plot(reg_2)

fig_11

We do not focus into the individual
effects of particular variables as we found them to be highly dependent
on the exact question asked and the set of data included, and since we
cannot ascribe any actual likelihood to any individual state of nature
simulated here.

@@

```{r}
